A Study of Common Bug Fix Patterns in Rust

### 2022-11-25 results.tex
static lifetime

\noindent\textbf{Description:} This change pattern removes the static keyword from a const variable declaration. This change can be applied using Clippy. A static lifetime of a variable indicates that the variable lives for the entire lifetime of the running program, and is not bound to a specific scope. If the presence of static is not required, it is better that to omit it, as keeping it might create complicated types in the program.

>>>>

\noindent\textbf{Description:} This change pattern removes the static keyword from a const variable declaration. This change can be applied using Clippy. A static lifetime associated with a variable indicates that the variable lives for the entire lifetime of the running program, and is not bound to a specific scope. If the presence of static is not required, it is better that to omit it, as keeping it might create complicated types in the program.
